How to measure the radial velocity of a star:\\The invariant-spectrum case

### 2022-02-02 paper/main.tex

% to-do list
% ----------
% - Synchronize to a git repository, and synchronize also the notebooks.
% - Look for all instances of HOGG, MB, and CITE.
% - Make an acronym command and fix CLRB and all other acronyms.
% - Be sure to discuss SNR in a continuum resolution element, as well as in a pixel.
%.- Make sure that, for any assumption that is explicitly tested, the forthcoming test is mentioned when the assumption is introduced.
% - Are we clear that we exponentiate the model to get the true data?

@@

% Math macros
\DeclareMathOperator{\CCF}{CCF}
\DeclareMathOperator{\E}{\mathbb{E}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\given}{\,|\,}
\newcommand{\lao}[1]{\boldsymbol{#1}}
\newcommand{\vy}{\lao{y}}
\newcommand{\vf}{\lao{f}}
\newcommand{\vC}{\lao{C}}
\newcommand{\unit}[1]{\mathrm{#1}}
\newcommand{\m}{\unit{m}}
\newcommand{\cm}{\unit{cm}}
\newcommand{\s}{\unit{s}}
\newcommand{\cmps}{\cm\,s^{-1}}
\newcommand{\mps}{\m\,s^{-1}}

@@

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{data.pdf}
    \end{center}
    \caption{Several example toy-data spectra, generated according to the rules described in the main text.
    At each epoch the true spectrum has the same overall shape; the only differences from epoch to epoch are from Doppler-shift changes and shot noise.\label{fig:data}}
  \end{mdframed}
\end{figure}

@@

HOGG: Maybe show that the wrong template (like missing some lines) gives less-good RVs.

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    [HOGG: NEED FIGURE HERE]
    \end{center}
    \caption{HOGG: A visualization of part of the binary mask.\label{fig:binarymask}}
  \end{mdframed}
\end{figure}

@@

HOGG: Demonstration with the toy data: FT the data, filter, shift and average, get RVs, shift and average again, and so on.

@@

@@

We opened (\secref{sec:assumptions}) with a long list of restrictive assumptions.
Here we perform experiments in which we make the data weakly incompatible with the assumptions and look at how the radial-velocity measurements are affected.

>>>>

% to-do list
% ----------
% - Look for all instances of HOGG, MB, and CITE.
% - Make an acronym command and fix CLRB and all other acronyms.
% - Be sure to discuss SNR in a continuum resolution element, as well as in a pixel.
%.- Make sure that, for any assumption that is explicitly tested, the forthcoming test is mentioned when the assumption is introduced.
% - Are we clear that we exponentiate the model to get the true data expectation?
% - Are we consistent in our use of Doppler shift, radial velocity, and redshift and so on?
% - Are we sensible in our use of first person?

@@

% Math macros
\DeclareMathOperator{\CCF}{CCF}
\DeclareMathOperator{\E}{\mathbb{E}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\given}{\,|\,}
\newcommand{\lao}[1]{\boldsymbol{#1}}
\newcommand{\vy}{\lao{y}}
\newcommand{\vf}{\lao{f}}
\newcommand{\vC}{\lao{C}}
\newcommand{\unit}[1]{\mathrm{#1}}
\newcommand{\m}{\unit{m}}
\newcommand{\cm}{\unit{cm}}
\newcommand{\km}{\unit{km}}
\newcommand{\s}{\unit{s}}
\newcommand{\cmps}{\cm\,\s^{-1}}
\newcommand{\mps}{\m\,\s^{-1}}
\newcommand{\kmps}{\km\,\s^{-1}}

@@

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/data.png}
    \end{center}
    \caption{Several example toy-data spectra, generated according to the rules described in the main text.
    At each epoch the true spectrum has the same overall shape; the only differences from epoch to epoch are from Doppler-shift changes and shot noise.\label{fig:data}}
  \end{mdframed}
\end{figure}

@@

HOGG: Maybe show that the wrong template (like missing some lines) gives less-good RVs?? Or move this to \secref{sec:sensitivity}??

@@

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/binarymask.png}
    \end{center}
    \caption{HOGG: A visualization of part of the binary mask.\label{fig:binarymask}}
  \end{mdframed}
\end{figure}

@@

Empirical templates can be created by interpolating spectra to a common logarithmic wavelength grid and averaging.
Interpolations wwre performed with cubic splines.
With an empirical template in hand, cross-correlation doppler shifts can be estimated, updating the beliefs about the spectra rest frames, and then the templates can be re-made.
This process can be iterated to convergence.
In this process, the initialization matters.
In making the results in this \sectionname, we initialized at the wrong binary-mask results shown in \figref{fig:bccfrvswrong}, not at good radial-velocities, and yet the results are excellent.
That is, we didn't cheat.
We show the empirical-spectrum cross-correlation radial-velocity results in \figref{fig:empiricalrvs}

\begin{figure}[t]
  \begin{mdframed}
    \begin{center}
    [HOGG: NEED FIGURE HERE]
    \end{center}
    \caption{HOGG: Something that shows the empirical-spectrum CCFs deliver good RVs.\label{fig:empiricalrvs}}
  \end{mdframed}
\end{figure}

@@

HOGG: Note that there is no absolute velocity here.

@@

We opened (\secref{sec:assumptions}) with a long list of restrictive assumptions.
Here we perform experiments in which we make the data weakly incompatible with some of these assumptions and look at how the radial-velocity measurements are affected.
